---
title: "Project Proposal"
author: "Guilherme Zanatta Tocchetto"
date: "9 de novembro de 2018"
output:
  pdf_document: default
  html_document: default
---

## Dataset Information

The choosen dataset contains all the details of the applications on Google Play. There are 13 features that describe a given app, the information given in each row of the dataset includes:

 - The name of the app;
 - The category that the app belongs to;
 - The overall user rating of the app;
 - The number of revews of the app;
 - The size of the app;
 - The number of users that downloaded/installed the app;
 - If the app is paid of free;
 - The price of the app;
 - The age group that the app is targeted at;
 - It's genre;
 - The date that it was last updated;
 - The current version of the app available on PlayStore;
 - The minimum required Android version to run the app.

```{r init, include=FALSE, echo=FALSE}
library(readr)
URL <- "data-set/googleplaystore.csv"
df <- read_delim(URL, delim=",")
df
#Delete inconsistent data
df <- na.omit(df)
df
```


## Questions to answer

- Which category of apps is the most downloaded?
<!--I've changed the question because the installs collumn doesn't provide a consistent value-->
- How many apps are there in each category?
```{r graficoCat, echo=FALSE, fig.align='center', fig.width=6, fig.height=5}

df$Category <- gsub('_', ' ', df$Category)

library(ggplot2);
  ggplot(df,
  aes(Category,..count..))+
  geom_point(stat = "count", size = 1)+
  scale_y_continuous(name ="Number of Applications", breaks=seq(0,1750,100))+
  theme(axis.text.x = element_text(angle = 65, hjust = 1))+
  labs(title="Number of Applications for Each Category", 
       subtitle="From kaggle.com", 
       caption="Google Play Store Apps")

#library(ggplot2);
  #ggplot(df,
  #aes(Category,..count..))+
  #geom_point(aes(col=Category), stat = "count", size = 1)+
  #scale_y_continuous(name ="Number of Accidents", breaks=seq(0,1750,50))+
  #theme(axis.title.x=element_blank(),
        #axis.text.x=element_blank(),
        #axis.ticks.x=element_blank())
```

- How many categories have the mean rating grater than 4?

```{r graficoRat4,  echo=FALSE, fig.align='center', fig.width=6, fig.height=7}
library(dplyr, warn.conflicts = FALSE)
library(magrittr)

catNames <- c("ART AND DESIGN","AUTO AND VEHICLES","BEAUTY","BOOKS AND REFERENCE","BUSINESS","COMICS","COMMUNICATION","DATING","EDUCATION","ENTERTAINMENT","EVENTS", "FAMILY", "FINANCE","GAME","HEALTH AND FITNESS","HOUSE AND HOME","LIBRARIES AND DEMO","LIFESTYLE","MAPS AND NAVIGATION","MEDICAL","NEWS AND MAGAZINES","PARENTING","PERSONALIZATION","PHOTOGRAPHY","PRODUCTIVITY","SHOPPING","SOCIAL","SPORTS","TOOLS","TRAVEL AND LOCAL","VIDEO PLAYERS","WEATHER")

ratingAverage <- c()

dfRate <- data.frame("Categories"=catNames)
dfRate$Ratings <- NA

for (i in 1:32) {
  n_rows = df %>% filter(Category==catNames[i]) %>% tally()
  sum = df %>% filter(Category==catNames[i]) %>% select(Rating) %>% sum()
  average = sum / n_rows
  dfRate$Ratings[i] <- average[1,1]
}

library(ggplot2);
  ggplot(dfRate,
  aes(Ratings, Categories))+geom_point()+
  labs(title="Apps Categories Vs Apps Ratings", 
       subtitle="From kaggle.com", 
       caption="Google Play Store Apps")
```

- Is the content rating related to the number of downloads/installs?
<!--I've changed the question because the installs collumn doesn't provide a consistent value-->
- Is the content rating related to the number of reviews?

```{r graficoRateXRev, echo=FALSE, fig.align='center', fig.width=8.5, fig.height=5}



dfRate$Reviews <- NA

for (i in 1:32) {
  n_rows = df %>% filter(Category==catNames[i]) %>% tally()
  sum = df %>% filter(Category==catNames[i]) %>% select(Reviews) %>% sum()
  average = sum / n_rows
  dfRate$Reviews[i] <- average[1,1]
}

#dfRate

type <-c(dfRate$Ratings, dfRate$Reviews)
#type

p <-ggplot(dfRate, aes(Categories, Ratings))
p +geom_bar(stat = "identity", aes(fill = Reviews), position = "dodge") +
  geom_text(aes(label=round(Ratings, 2)), vjust=1.6, color="white", size=2.1)+
  xlab("Applications") + ylab("Rating") +
  ggtitle("Rating/Reviews") +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 65, hjust = 1))+
  labs(title="Apps Ratings Vs Apps Reviews", 
       subtitle="From kaggle.com", 
       caption="Google Play Store Apps")



```

- How does the type of the app (paid/free) relate to the rating?
É possível ver que o ser pago ou gratz não influencia na percepção do usuário em relação a qualidade do aplicativo

```{r graficoTRev, echo=FALSE, fig.align='center', fig.width=6, fig.height=4}

dfTR <- matrix(0, ncol = 2, nrow = 2)
dfTR <- data.frame(dfTR)
n_rows = df %>% filter(Type=='Paid') %>% tally()
sum = df %>% filter(Type=='Paid') %>% select(Rating) %>% sum()
average = sum / n_rows
dfTR$Type[1] <- 'Paid'
dfTR$Rating[1] <- average[1,1]

n_rows = df %>% filter(Type=='Free') %>% tally()
sum = df %>% filter(Type=='Free') %>% select(Rating) %>% sum()
average = sum / n_rows
dfTR$Type[2] <- 'Free'
dfTR$Rating[2] <- average[1,1]

p <-ggplot(dfTR, aes(Type, Rating))
p +geom_bar(stat = "identity", aes(fill = Type), position = "dodge") +
  geom_text(aes(label=round(Rating, 2)), vjust=1.6, color="black", size=3.5)+
  xlab("") + ylab("Rating") +
  labs(title="Apps Vs Apps Reviews", 
       subtitle="From kaggle.com", 
       caption="Google Play Store Apps")
```